
%Homework must be printed, neat and stapled (\textbf{it cannot be emailed to me}) but if you use \LaTeX~it can be pushed to your own repository (see \qu{Homework \LaTeX~bonus points} section below) and I will grade it digitally. Homework can be given to me in class or delivered under my office door (KY 604).

%Graded homework will be returned in class. Regrades are handled during office hours or right after class is over. Scores for homeworks are finalized one week after the graded copies are handed back. Thereafter there will be no changes and no re-grading. Do not delay checking your graded homeworks. I am not perfect and I do make mistakes. It is your obligation to find these mistakes and report them.

\textbf{During this pandemic, homework must be handed in by emailing it to me as a PDF. You must do one of two things:}

\begin{itemize}
\item \textbf{Print out the homework and handwrite your answers in the alotted space for each question. Then scan your homework as a PDF. There are a ton of good photo-PDF apps for both iPhone and droid. }
\item \textbf{Open the PDF on your device and use a PDF-editing program to electronically handwrite your answers and save the PDF.}
\end{itemize}

\textbf{I will NOT accept homework that is not atop the original rendered homework PDF file. Remember to write your name. There are no regrades during this pandemic semester.}

You are encouraged to seek help from me if you have questions. After class and office hours are good times. \ingreen{You are highly recommended to work with each other and help each other.} \inred{You must, however, submit your own solutions, \textit{with your own write-up} and in \textit{your own words}. There can be no collaboration on the actual \textit{writing}. Failure to comply will result in severe penalties.} The university honor code is something I take seriously and I send people to the Dean every semester for violations.